---
title: "Steps for using Python in RStudio on Windows 10"
author: "Lucky Mehra"
date: "2/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I used Kristopher Overholt's [awesome guide](https://support.rstudio.com/hc/en-us/articles/360023654474-Installing-and-Configuring-Python-with-RStudio) to configure Python in RStudio. However, there were some steps that I had to tweak slightly to make it work on Windows 10 operating system.

I will only list the steps that I had to do differently. I used Anaconda Prompt
for installing `virtualenv` (step 1 and step 2).

### Step 3

Instead of `source python/bin/activate` use `source python/Scripts/activate`. Also,
enter `source python/Scripts/activate` in the Terminal tab (next to the Console)
tab. I am using *Git Bash* as my RStudio Terminal.

### Step 5

Inside .Rprofile file, the content should be

```
Sys.setenv(RETICULATE_PYTHON = "python/Scripts/python.exe")
```

Everything else should be same as described the guide from [RStudio Support](https://support.rstudio.com/hc/en-us/articles/360023654474-Installing-and-Configuring-Python-with-RStudio)

### Test python run

```{python}
import pandas as pd

d = {'col1': [1, 2], 'col2': [3, 4]}
df = pd.DataFrame(data=d)
df
type(df)
```

Access python dataframe in an R chunk

```{r}
library(reticulate)
df_in_r <- py$df

df_in_r

class(df_in_r)
```



```{r}
sessionInfo()
```

